# Download

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Desktop Client

We build the desktop client of Hiplot based on the [Electron](https://www.electronjs.org/). The demo data and UI components are fixed in the desktop client under the given version.

Latest release version:

```{r echo = FALSE}
library(data.table)
library(stringr)
download_dir <- getOption("hiplot.download_dir")
latest <- readLines(file.path(download_dir, "desktop", "latest/version"))
md5sum <- fread(cmd = sprintf("cat %s/desktop/%s/md5sum | sed 's;  ;\t;'",
  download_dir, latest),
  sep = "\t", data.table = FALSE, header = FALSE)
base_dir <- sprintf("https://hiplot.com.cn/download/desktop/%s", latest)
md5sum[,"Date"] <- as.Date(file.info(md5sum[,2])$mtime, "%d%b%Y")
md5sum[,"Size"] <- sapply(file.info(md5sum[,2])$size, function(x) {
  utils:::format.object_size(x, "auto")
})
md5sum[,"URL"] <- file.path(base_dir, basename(md5sum[,2]))
md5sum[,"File"] <- basename(md5sum[,2])
md5sum <- md5sum[md5sum$File != "md5sum",]
colnames(md5sum)[1] <- "MD5"
md5sum[,"File"] <- sprintf("[%s](%s)", md5sum[,"File"], md5sum[,"URL"])
md5sum <- md5sum[,c("File", "Size", "Date", "MD5")]
knitr::kable(md5sum)
```

Old release version (v0.1.0):

**Linux:**

- [Hiplot_Desktop_0.1.0_Linux_x86_64.AppImage](https://hiplot.com.cn/download/desktop/v0.1.0/Hiplot_Desktop_0.1.0_Linux_x86_64.AppImage)
- [Hiplot_Desktop_0.1.0_Linux_amd64.snap](https://hiplot.com.cn/download/desktop/v0.1.0/Hiplot_Desktop_0.1.0_Linux_amd64.snap)

**Windows:**

- [Hiplot_Desktop_0.1.0_Windows.exe](https://hiplot.com.cn/download/desktop/v0.1.0/Hiplot_Desktop_0.1.0_Windows.exe)

**MAC OSX**

- [Hiplot_Desktop_0.1.0_Darwin.dmg](https://hiplot.com.cn/download/desktop/v0.1.0/Hiplot_Desktop_0.1.0_Darwin.dmg)

## hctl

hctl is the command-line client of Hiplot website. It can be used to draw plots without the web environment.

Latest release version (v0.1.3):

**Linux:**

- [hctl_0.1.3_Linux_64-bit.tar.gz](https://hiplot.com.cn/download/hctl/v0.1.3/hctl_0.1.3_Linux_64-bit.tar.gz)
- [hctl_0.1.3_Linux_32-bit.tar.gz](https://hiplot.com.cn/download/hctl/v0.1.3/hctl_0.1.3_Linux_32-bit.tar.gz)

**MAC OSX:**

- [hctl_0.1.3_Darwin_64-bit.tar.gz](https://hiplot.com.cn/download/hctl/v0.1.3/hctl_0.1.3_Darwin_64-bit.tar.gz)


**Windows:**
- [hctl_0.1.3_Windows_64-bit.tar.gz](https://hiplot.com.cn/download/hctl/v0.1.3/hctl_0.1.3_Windows_64-bit.tar.gz)
- [hctl_0.1.3_Windows_32-bit.tar.gz](https://hiplot.com.cn/download/hctl/v0.1.3/hctl_0.1.3_Windows_32-bit.tar.gz)

It is required to login Hiplot server first using the `hctl login` command. `hctl plot` command can be used to draw plots by using the parameter file and data files.

Demo input files of hctl can be download from here: [demo.tar.gz](https://hiplot.com.cn/download/hctl/_demo.tar.gz).

```bash
## Linux 64 Demo
mkdir /tmp/hiplot
cd /tmp/hiplot
wget https://hiplot.com.cn/download/hctl/v0.1.3/hctl_0.1.3_Linux_64-bit.tar.gz
wget https://hiplot.com.cn/download/hctl/_demo.tar.gz

tar -xzvf hctl_0.1.3_Linux_64-bit.tar.gz
tar -xzvf _demo.tar.gz

./hctl login

# only input data files
./hctl plot -c _demo/heatmap/config.json -t heatmap -d _demo/heatmap/countData.txt,_demo/heatmap/sampleInfo.txt,_demo/heatmap/geneInfo.txt -o /tmp/hiplot-pure-data-mode

# only use remote files
./hctl plot -c _demo/heatmap/config2.json -t heatmap -o /tmp/hiplot-pure-remote-data-mode

# mixed usage
./hctl plot -c _demo/heatmap/config3.json -t heatmap -d _demo/heatmap/countData.txt,,_demo/heatmap/geneInfo.txt -o /tmp/hiplot-mixed-mode

# hiplot exported param
./hctl plot -p _demo/heatmap/params.json -t heatmap -o /tmp/hiplot-params-mode
```

### Main Interface

```{bash message=FALSE, warning=FALSE, echo=FALSE}
cd /tmp
hctl -h
```

### Plot Interface

```{bash message=FALSE, warning=FALSE, echo=FALSE}
cd /tmp
hctl plot -h
```
