# Download

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Desktop Client

We build the desktop client of Hiplot based on the [Electron](https://www.electronjs.org/). The demo data and UI components are fixed in the desktop client under the given version.

Latest release version:

```{r echo = FALSE}
source("../scripts/download_table.R")
download_table("desktop", "versionDesktop")
```

Other releases of desktop client: [here](https://hiplot.com.cn/download/desktop)

## hctl

hctl is the command-line client of Hiplot website. It can be used to draw plots without the web environment.

Latest release version (v0.1.4):

```{r echo = FALSE}
download_table("hctl", "versionTerminal")
```

Other releases of hctl: [here](https://hiplot.com.cn/download/hctl)

It is required to login Hiplot server first using the `hctl login` command. `hctl plot` command can be used to draw plots by using the parameter file and data files.

Demo input files of hctl can be download from here: [demo.tar.gz](https://hiplot.com.cn/download/hctl/_demo.tar.gz).

```bash
## Linux 64 Demo
mkdir /tmp/hiplot
cd /tmp/hiplot
wget https://hiplot.com.cn/download/hctl/v0.1.4/hctl_0.1.4_Linux_64-bit.tar.gz
wget https://hiplot.com.cn/download/hctl/_demo.tar.gz

tar -xzvf hctl_0.1.4_Linux_64-bit.tar.gz
tar -xzvf _demo.tar.gz

hctl login

# only input data files
hctl plot -c _demo/heatmap/config.json -t heatmap -d _demo/heatmap/countData.txt,_demo/heatmap/sampleInfo.txt,_demo/heatmap/geneInfo.txt -o /tmp/hiplot-pure-data-mode

# only use remote files
hctl plot -c _demo/heatmap/config2.json -t heatmap -o /tmp/hiplot-pure-remote-data-mode

# mixed usage
hctl plot -c _demo/heatmap/config3.json -t heatmap -d _demo/heatmap/countData.txt,,_demo/heatmap/geneInfo.txt -o /tmp/hiplot-mixed-mode

# hiplot exported params
hctl plot -p _demo/heatmap/params.json -t heatmap -o /tmp/hiplot-params-mode

# hiplot config 和 plot 命令联合
## show hctl supported plugins
hctl config -l
## download basic/tsne params
hctl config basic/tsne
## draw tsne graphics
hctl plot -p basic-tsne-params.json -o /tmp/hiplot-tsne
```

### Main Interface

```{bash message=FALSE, warning=FALSE, echo=FALSE}
cd /tmp
hctl -h
```

### Plot Interface

```{bash message=FALSE, warning=FALSE, echo=FALSE}
cd /tmp
hctl plot -h
```
